---
title: "SRCD 2019 Symposium: Religious & metaphysical concepts (Srinivasan)"
output: 
  html_notebook:
    toc: true
    toc_float: true
---

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 3, fig.asp = 0.67)
```

```{r}
# load required libraries
library(tidyverse)
library(langcog) # source: https://github.com/langcog/langcog-package
library(psych)
library(lme4)
library(cowplot)

# set theme for ggplots
theme_set(theme_bw())
```

```{r, include = F}
source("./scripts/max_factors_efa.R")
source("./scripts/plot_fun_beetles.R")
source("./scripts/reten_fun.R")
source("./scripts/clean_fun.R")
```

# Data preparation

```{r, include = F}
question_key <- read.csv("/Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DEVELOPMENTAL TASKS/beetles:dimkid:factors/design/beetles cb.csv")
```

```{r, include = F, warning = FALSE}
# US adults PILOT
d_us_ad_pilot_raw <- read.csv("/Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DEVELOPMENTAL TASKS/beetles:dimkid:factors/analysis/_US pilot/beetles_pilot2_tidy.csv")
d_us_ad_pilot <- d_us_ad_pilot_raw %>%
  filter(scale == "beetles") %>%
  distinct(subid, character, question, response) %>%
  filter(!question %in% c("bleed", "mind", "soul")) %>%
  mutate(question = recode(question,
                           "add_subtract" = "add and subtract numbers",
                           "angry" = "get angry",
                           # "bleed" = "bleed when they touch something sharp",
                           "choose" = "choose what to do",
                           "figure_out" = "figure out how to do things",
                           "guilty" = "feel guilty",
                           "happy" = "feel happy",
                           "hear" = "hear things",
                           "hungry" = "get hungry",
                           "hurt_feelings" = "get hurt feelings",
                           "love" = "feel love",
                           # "mind" = "have minds",
                           "pain" = "feel pain",
                           "pray" = "pray", 
                           "proud" = "feel proud",
                           "remember" = "remember things",
                           "sad" = "feel sad",
                           "scared" = "feel scared",
                           "sense_far" = "sense when things are far away",
                           "sense_temp" = "sense temperatures",
                           "shy" = "feel shy",
                           "sick" = "feel sick, like when you feel like you might vomit",
                           "smell" = "smell things",
                           # "soul" = "have souls",
                           "think" = "think about things",
                           "tired" = "feel tired")) %>%
  spread(question, response) %>%
  select(-subid) %>%
  mutate(subid = paste("us_ad",
                       10001:(10000+length(levels(factor(d_us_ad_pilot_raw$subid)))),
                       "target",
                       character,
                       sep = "_")) %>%
  column_to_rownames("subid") %>%
  select(-`add and subtract numbers`, -character)
```

```{r, include = F, warning = FALSE}
## US adults: NOT YET RUN
## US children: NOT YET RUN

## GH adults: NOT YET RUN
d_gh_ad <- read.csv("/Users/kweisman/Desktop/TEMP/TEMP_GHANA_2018/beetles_ghana_adults_tidy_2018-08-12.csv") %>% clean_fun(key = question_key, ex_addsub = T, site = "gh", age = "ad")
## GH children
d_gh_ch <- read.csv("/Users/kweisman/Desktop/TEMP/TEMP_GHANA/beetles_ghana_tidy_2017-07-12.csv") %>% clean_fun(key = question_key, ex_addsub = T, site = "gh", age = "ch")
d_gh_ch_fante <- read.csv("/Users/kweisman/Desktop/TEMP/TEMP_GHANA_2018/beetles_ghana_fante_children_tidy_2018-07-19.csv")[-1] %>% 
  rename(subnum = subid) %>% 
  filter(grepl("fante", tolower(language_home)) | grepl("twi", tolower(language_home))) %>%
  clean_fun(key = question_key, ex_addsub = T, site = "gh", age = "ch")

## CH adults: NOT YET RUN
## CH children: NOT YET RUN

## TH adults
d_th_ad <- read.csv("/Users/kweisman/Desktop/TEMP/TEMP_THAILAND/beetles_thailand_adults_tidy_2018-05-09.csv") %>% clean_fun(key = question_key, ex_addsub = T, site = "th", age = "ad")
## TH children
d_th_ch <- read.csv("/Users/kweisman/Desktop/TEMP/TEMP_THAILAND/beetles_thailand_children_tidy_2018-05-09.csv") %>% clean_fun(key = question_key, ex_addsub = T, site = "th", age = "ch")

## VT adults
d_vt_ad <- read.csv("/Users/kweisman/Desktop/TEMP/TEMP_VANUATU/beetles_vanuatu_adults_tidy_2018-05-09.csv") %>% clean_fun(key = question_key, ex_addsub = T, site = "vt", age = "ad")
## VT children
d_vt_ch <- read.csv("/Users/kweisman/Desktop/TEMP/TEMP_VANUATU/beetles_vanuatu_children_tidy_2018-05-09.csv") %>% clean_fun(key = question_key, ex_addsub = T, site = "vt", age = "ch")
```

```{r}
d_all <- # d_us_ad_pilot %>% rownames_to_column("subid") %>%
  d_gh_ad %>% rownames_to_column("subid") %>%
  full_join(d_gh_ch %>% rownames_to_column("subid")) %>%
  full_join(d_th_ad %>% rownames_to_column("subid")) %>%
  full_join(d_th_ch %>% rownames_to_column("subid")) %>%
  full_join(d_vt_ad %>% rownames_to_column("subid")) %>%
  full_join(d_vt_ch %>% rownames_to_column("subid")) %>%
  column_to_rownames("subid")
```

# Shared conceptual structure

Pooling all participants from all sites together into a common factor structure.

## Parallel analysis

### How many factors to retain?

```{r}
reten_all_PA <- fa.parallel(d_all, plot = F); reten_all_PA
reten_all_par <- reten_all_PA$nfact
```

### What are these factors?

```{r}
efa_all_par <- fa(d_all, nfactors = reten_all_par, rotate = "oblimin",
                  scores = "tenBerge", impute = "median")
```

```{r, fig.width = 4.2, fig.asp = 0.7}
heatmap_fun(efa_all_par, 
            factor_names = c("COGNITIVE", "BODILY", 
                             "SOCIAL-EMOTIONAL", "[other]")) + 
  labs(title = "Factor loadings (data pooled across all samples)")
```

### Which capacities are attributed to which targets?

#### Factor scores

```{r, fig.width = 5, fig.asp = 0.8}
scoresplot_fun(efa_all_par, target = "all",
               factor_names = c("COGNITIVE", "BODILY", 
                                "SOCIAL-EMOTIONAL", "[other]")) + 
  labs(title = "Factor scores (by sample, factor, and target entity)",
       subtitle = "All targets")
```

```{r, fig.width = 3.5, fig.asp = 0.8}
scoresplot_fun(efa_all_par, target = c("ghosts", "God", "children"),
               factor_names = c("COGNITIVE", "BODILY",
                                "SOC.-EMO.", "[other]")) + 
  labs(title = "Factor scores (by sample, factor, and target entity)",
       subtitle = "Human and 'supernatural' targets only")
```

```{r, fig.width = 5, fig.asp = 1}
itemsplot_fun(efa_all_par, target = c("ghosts", "God", "children")) +
  labs(title = "Parallel Analysis")
```

#### Summary scores

```{r}
factors_par <- efa_all_par$loadings[] %>%
  data.frame() %>%
  rownames_to_column("capacity") %>%
  gather(factor, loading, -capacity) %>%
  group_by(capacity) %>%
  top_n(1, loading) %>%
  ungroup() %>%
  arrange(factor, desc(loading)) %>%
  mutate(order = 1:nrow(.))

factors_par_howmany <- factors_par %>%
  count(factor)

factors_par_culled <- factors_par %>%
  group_by(factor) %>%
  top_n(min(factors_par_howmany$n), loading) %>%
  ungroup() %>%
  arrange(factor, desc(loading)) %>%
  mutate(order = 1:nrow(.))

scores_par_prelim <- d_all %>%
  rownames_to_column("site_age_subid_target_entity") %>%
  gather(capacity, response, -site_age_subid_target_entity) %>%
  mutate(site = gsub("_.*$", "", site_age_subid_target_entity),
         age = gsub("_.*$", "", gsub("^.._", "", site_age_subid_target_entity)),
         subid = gsub("_target.*$", "", site_age_subid_target_entity),
         target = gsub("^.*target_", "", site_age_subid_target_entity)) %>%
  mutate(target = case_when(target == "pigs" ~ NA_character_,
                            target == "NA" ~ NA_character_,
                            target == "crickets" ~ "beetles",
                            TRUE ~ target)) %>%
  mutate(site = factor(site, levels = c("us", "gh", "th", "ch", "vt"),
                       labels = c("US", "Ghana", "Thailand", "China", "Vanuatu")),
         age = factor(age, levels = c("ad", "ch"),
                      labels = c("adults", "children")),
         target = factor(target,
                         levels = c("rocks", "flowers", "cell phones", 
                                    "beetles", "chickens", "mice", 
                                    "dogs", "children", 
                                    "ghosts", "God"))) %>%
  select(-site_age_subid_target_entity) %>%
  full_join(factors_par_culled) %>%
  # full_join(factors_par) %>%
  mutate(factor = factor(factor, levels = c("MR2", "MR1", "MR3", "MR4"),
                         labels = c("BODILY", "COGNITIVE", 
                                    "SOCIAL-EMOTIONAL", "[other]"))) %>%
  filter(!is.na(target), !is.na(factor)) %>%
  distinct()

scores_par <- scores_par_prelim %>%
  group_by(site, age, subid, target, factor) %>%
  summarise(score = mean(response, na.rm = T)) %>%
  ungroup()

scores_par_mb <- scores_par %>% 
  group_by(site, age, target, factor) %>%
  multi_boot_standard(col = "score", na.rm = T) %>%
  ungroup()
```

```{r}
# calculate reliability
scores_par_prelim_wide <- scores_par_prelim %>%
  full_join(factors_par_culled) %>%
  filter(!is.na(factor), !is.na(subid)) %>% 
  arrange(factor, desc(loading)) %>%
  select(subid, capacity, response) %>%
  spread(capacity, response) %>%
  select(subid, factors_par_culled$capacity) %>%
  column_to_rownames("subid")

# BODILY
alpha(scores_par_prelim_wide[5:8])$total

# "COGNITIVE"
alpha(scores_par_prelim_wide[1:4])$total

# "SOCIAL-EMOTIONAL"
alpha(scores_par_prelim_wide[9:12])$total
```


```{r, fig.width = 5, fig.asp = 0.8}
ggplot(scores_par, aes(x = target, y = score, color = factor)) +
  facet_grid(cols = vars(site, age), rows = vars(factor)) +
  geom_jitter(height = 0.02, width = 0.2, alpha = 0.2, show.legend = F) +
  geom_pointrange(data = scores_par_mb,
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  fatten = 2, color = "black") +
  scale_color_brewer(palette = "Set1") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r, fig.width = 3.5, fig.asp = 0.8}
ggplot(scores_par %>% filter(target %in% c("children", "ghosts", "God")), 
       aes(x = target, y = score, color = factor)) +
  facet_grid(cols = vars(site, age), rows = vars(factor)) +
  geom_jitter(height = 0.02, width = 0.2, alpha = 0.25, show.legend = F) +
  geom_pointrange(data = scores_par_mb %>%
                    filter(target %in% c("children", "ghosts", "God")),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  fatten = 2, color = "black") +
  scale_color_brewer(palette = "Set1") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```


## Minimizing BIC

### How many factors to retain?

```{r}
reten_all_BIC <- VSS(d_all, plot = F); reten_all_BIC
reten_all_bic <- data.frame(reten_all_BIC$vss.stats %>% rownames_to_column("nfact") %>% top_n(-1, BIC))$nfact %>% as.numeric()
```

### What are these factors?

```{r}
efa_all_bic <- fa(d_all, nfactors = reten_all_bic, rotate = "oblimin",
                  scores = "tenBerge", impute = "median")
```

```{r, fig.width = 4.5}
heatmap_fun(efa_all_bic, 
            factor_names = c("COGNITIVE", "BODILY", "SOCIAL-EMOTIONAL", "other")) + 
  # labs(title = "Minimizing BIC")
  labs(x = "Figure 1: Shared conceptual structure") +
  theme(axis.title.x = element_text(hjust = 0)) +
  guides(fill = guide_colorbar("factor loading", barheight = 15))
```

### Which capacities are attributed to which targets?

```{r, fig.width = 5, fig.asp = 1}
scoresplot_fun(efa_all_bic, target = "all", highlight = "supernatural",
            factor_names = c("COGNITIVE", "BODILY", "SOCIAL-EMOTIONAL", "other")) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1,
                                   color = c(rep("black", 8),
                                             rep("#984ea3", 2)),
                                   face = c(rep("plain", 8),
                                            rep("bold", 2)))) +
  scale_fill_manual(values = c("#e41a1c", "#4daf4a", "#377eb8", "gray")) +
  # labs(title = "Minimizing BIC")
  labs(title = "Figure 2: Factor scores")
```

```{r, fig.width = 3.5, fig.asp = 1}
scoresplot_fun(efa_all_bic, target = c("ghosts", "God", "children")) + 
  # scale_fill_manual(values = c("#e41a1c", "#4daf4a", "#377eb8")) +
  labs(title = "Minimizing BIC")
```

```{r, fig.width = 5, fig.asp = 1}
itemsplot_fun(efa_all_bic, target = c("ghosts", "God", "children")) + 
  labs(title = "Minimizing BIC")
```



## Preset criteria

### How many factors to retain?

```{r}
reten_all_k <- reten_fun(d_all, rot_type = "oblimin"); reten_all_k
```

### What are these factors?

```{r}
efa_all_k <- fa(d_all, nfactors = reten_all_k, rotate = "oblimin",
                  scores = "tenBerge", impute = "median")
```

```{r, fig.width = 3, fig.asp = 2}
heatmap_fun(efa_all_k) + 
  labs(title = "Preset criteria (Weisman et al., 2017)")
```

### Which capacities are attributed to which targets?

```{r, fig.width = 6, fig.asp = 0.8}
scoresplot_fun(efa_all_k, target = "all") + 
  labs(title = "Preset criteria (Weisman et al., 2017)")
```

```{r, fig.width = 3, fig.asp = 1.5}
scoresplot_fun(efa_all_k, target = c("ghosts", "God", "children")) + 
  labs(title = "Preset criteria (Weisman et al., 2017)")
```

```{r, fig.width = 5, fig.asp = 1}
itemsplot_fun(efa_all_k, target = c("ghosts", "God", "children")) + 
  labs(title = "Preset criteria (Weisman et al., 2017)")
```


## 3 factors

### What are these factors?

```{r}
efa_all_3 <- fa(d_all, nfactors = 3, rotate = "oblimin",
                scores = "tenBerge", impute = "median")
```

```{r, fig.width = 4, fig.asp = 0.6}
heatmap_fun(efa_all_3, 
            factor_names = c("COGNITIVE", "BODILY", "SOCIAL-EMOTIONAL")) + 
  labs(x = "Shared concpetual structure") +
  theme(axis.title.x = element_text(hjust = 0))
  # labs(title = "Preset criteria (Weisman et al., 2017)")
```

### Which capacities are attributed to which targets?

```{r, fig.width = 6, fig.asp = 0.67}
scoresplot_fun(efa_all_3, target = "all", highlight = "supernatural",
               factor_names = c("COGNITIVE", "BODILY", "SOCIAL-EMOTIONAL")) +
  scale_fill_manual(values = c("#e41a1c", "#4daf4a", "#377eb8")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1,
                                   color = c(rep("black", 8),
                                             rep("#984ea3", 2)),
                                   face = c(rep("plain", 8),
                                            rep("bold", 2))))
```

```{r, fig.width = 3, fig.asp = 1.5}
scoresplot_fun(efa_all_3, target = c("ghosts", "God", "children")) + 
  labs(title = "Preset criteria (Weisman et al., 2017)")
```

```{r, fig.width = 5, fig.asp = 1}
itemsplot_fun(efa_all_3, target = c("ghosts", "God", "children")) + 
  labs(title = "Preset criteria (Weisman et al., 2017)")
```


# Comparing conceptual structures

We'll extract 4 factors from all samples, to keep things simple.

```{r}
efa_us_ad_4 <- fa(d_us_ad_pilot, nfactors = 4, rotate = "oblimin")
efa_gh_ad_4 <- fa(d_gh_ad, nfactors = 4, rotate = "oblimin")
efa_gh_ch_4 <- fa(d_gh_ch, nfactors = 4, rotate = "oblimin")
efa_th_ad_4 <- fa(d_th_ad, nfactors = 4, rotate = "oblimin")
efa_th_ch_4 <- fa(d_th_ch, nfactors = 4, rotate = "oblimin")
efa_vt_ad_4 <- fa(d_vt_ad, nfactors = 4, rotate = "oblimin")
efa_vt_ch_4 <- fa(d_vt_ch, nfactors = 4, rotate = "oblimin")
```

```{r}
plot_us_ad_4 <- heatmap_fun(efa_us_ad_4) + 
  guides(fill = "none") + 
  labs(x = "US: adults") +
  theme(axis.title.x = element_text(hjust = 0))

plot_gh_ad_4 <- heatmap_fun(efa_gh_ad_4) + 
  guides(fill = "none") + 
  labs(x = "Ghana: adults") +
  theme(axis.title.x = element_text(hjust = 0))

plot_gh_ch_4 <- heatmap_fun(efa_gh_ch_4) + 
  guides(fill = "none") + 
  labs(x = "Ghana: children") +
  theme(axis.title.x = element_text(hjust = 0))

plot_th_ad_4 <- heatmap_fun(efa_th_ad_4) + 
  guides(fill = "none") + 
  labs(x = "Thailand: adults") +
  theme(axis.title.x = element_text(hjust = 0))

plot_th_ch_4 <- heatmap_fun(efa_th_ch_4) + 
  guides(fill = "none") + 
  labs(x = "Thailand: children") +
  theme(axis.title.x = element_text(hjust = 0))

plot_vt_ad_4 <- heatmap_fun(efa_vt_ad_4) + 
  guides(fill = "none") + 
  labs(x = "Vanuatu: adults") +
  theme(axis.title.x = element_text(hjust = 0))

plot_vt_ch_4 <- heatmap_fun(efa_vt_ch_4) + 
  guides(fill = "none") + 
  labs(x = "Vanuatu: children") +
  theme(axis.title.x = element_text(hjust = 0))
```

```{r, fig.asp = 1.5}
plot_grid(#plot_us_ad_4, 
          plot_gh_ad_4, plot_gh_ch_4, plot_th_ad_4, 
          plot_th_ch_4, plot_vt_ad_4, plot_vt_ch_4, 
          ncol = 2, labels = c("A", "B", "C", "D", "E", "F", "G"))
```

# Counts

```{r}
paste("US adults:", nrow(d_us_ad_pilot))
paste("GH adults:", nrow(d_gh_ad))
paste("GH children:", nrow(d_gh_ch))
paste("TH adults:", nrow(d_th_ad))
paste("TH children:", nrow(d_th_ch))
paste("VT adults:", nrow(d_vt_ad))
paste("VT children:", nrow(d_vt_ch))

paste("Non-US:", sum(nrow(d_gh_ad), nrow(d_gh_ch),
                     nrow(d_th_ad), nrow(d_th_ch),
                     nrow(d_vt_ad), nrow(d_vt_ch)))
```

